Measuring the Inherent Readability of Five Common Programming Languages

### 2015-02-11 rmtw/a1/assignment_1.tex
More changes based on feedback

Google Sheets was decided upon as the appropriate tool of choice for our survey. It has a good reputation for use in surveys and it was recommended to us by Dr. Richard Berntsson Svensson. We also have prior experience the tool from previous research projects.
The questionnaire consists of structured and partially structured questions. The questions are followed by two code snippets per language mentioned previously with a scale requesting the respondent to rate whether they feel that the code is easy or difficult to read in the style of the Likert Scale. The questions were written with as little ambiguity as possible. They were field tested by colleagues in a small example of our survey. Examples of these questions can be found in table 1. The aforementioned chart shows how some of our independent variables, research questions and survey items correlate.
\newline

@@

\SubSection{Threats to Validity}
As in all research there are threats to the validity of the study being undertaken. Our largest threat would be the external validity of the data collected. The students were selected from the three current years studying at the University of Gothenburg. Most of the respondents indicated that they are in the first year of their studies and as such their inexperience could be a limiting factor on their answers to the survey. The students may also have had a bias for one of the languages; Java. So far, the students in the first year have been formally taught in only Java. This means that there is a lower chance they would be familiar with reading other language syntax other than java and as such they would be more likely to see Java favourably than others. We cannot therefore generalise that Java has higher readability than that of the other languages despite what the results show. 
\newline

>>>>

Google Sheets was decided upon as the appropriate tool of choice for our survey. It has a good reputation for use in surveys and it was recommended to us by Dr. Richard Berntsson Svensson. We also have prior experience the tool from previous research projects.
The questionnaire consists of structured and partially structured questions. The questions are followed by two code snippets per language mentioned previously with a scale requesting the respondent to rate whether they feel that the code is easy or difficult to read in the style of the Likert Scale. The questions were written with as little ambiguity as possible. They were field tested by colleagues in a small example of our survey. An example of one question used in the survey is as follows:

\newline

@@

\SubSection{Threats to Validity}
As in all research there are threats to the validity of the study being undertaken. Our largest threat would be the external validity of the data collected. The students were selected from the three current years studying at the University of Gothenburg. Most of the respondents indicated that they are in the first year of their studies and as such their inexperience could be a limiting factor on their answers to the survey. The students may also have had a bias for one of the languages; Java. So far, the students in the first year have been formally taught in only Java. This means that there is a lower chance they would be familiar with reading other language syntax other than Java and as such they would be more likely to see Java favourably than others. We cannot therefore generalise that Java has higher readability than that of the other languages despite what the results show. 
\newline
